### 2018-10-04 paper/paper.tex
update

  The \emph{queue size} $\size{\Q_{i}}$ of stage $i$ is defined as
  $\size{\Q_{i}} \defsym \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
  $i$. Note that in this subsection we set $i=1$.

@@

\begin{definition}
  We define the \emph{time span} $\ts(p)$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \ts(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
    \MS[t]{\text{seasonal stuff todo}} \tcom
  \end{align*}
  where $\zs$ can be used to select the confidence interval being considered.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate

@@

The reduce the impact of outliers we average the actual releases over $ts(p)$ values.

>>>>

  The \emph{queue size} $\size{\Q_{i}}$ of stage $i$ is defined as
  $\size{\Q_{i}} \defsym \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
  $i$. Note that for this subsection $i=1$.

@@

\begin{definition}
  We define the \emph{time span considered} $\tsc(p)$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \tsc(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
    \MS[t]{\text{seasonal stuff}} \tcom
  \end{align*}
  where $\zs$ can be used to select the confidence interval being considered. Thus under the
  assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule, $68.3\%$,
  $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$,
  and $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate

@@

The reduce the impact of outliers we average the actual releases over $\tsc{p}$ values.
